---
title: "Map display of earthquake data"
author: "Abdul Rasheed Narejo"
date: "02/09/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

- This presentation and associated [shiny app](https://narejo.shinyapps.io/shiny-app/) are final project Developing Data Products course of the Coursera [Data Science Specialisation](https://www.coursera.org/specializations/jhu-data-science).

- The project has two parts;
  - First, you will create a Shiny application and deploy it on Rstudio's servers.
  - Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

```{r, message = FALSE, echo=FALSE, warning=FALSE}
# load required libraries
library(plotly)
library(dplyr)
```

## Final result
- The Shiny app developed for this project is available at: https://narejo.shinyapps.io/shiny-app/
- The presentation is available at:
- The source code is avaiable at: https://github.com/arnarejo/CourseraDS-Shiny/

## Objective
For this project I have tried to create a shiny app that achieves following
- Use leaflet to plot global map with countries being highlighted
- Plot earthquake data for 2017 and 2018, provide details in the popup window and make circle size/color depending on the earthquake magnitude
- As a shiny app the user has option to modify selection based on a range of earthquake magnitude and years.
- As output, the app display map with pointers of earthquakes and histogram of frequency of quakes by magnitude.

## Load libraries/data
```{r}

```
